% !TeX root = Kavinpon Navapong_Resume.tex
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue!80!black,
    urlcolor=blue!80!black    
}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}


%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Kavinpon} \headerlastnamestyle{Navapong} \\
	\vspace{2mm}
	{\faEnvelope\ kavinpon@hotmail.com} | {\faMobile\ +66863266507} | {\faMapMarker\ Bangkok, Thailland} | {\faLinkedin\ linkedin.com/in/kavinpon}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Work Experience}
\begin{cventries}
	\cventry
	{Beam Mobility}
	{Fullstack Software Engineer}
	{Singapore (Remote)}
	{December 2022 - Present}
	{\begin{cvitems}
			\item {Collaborated with cross-functional teams to gather requirements, design system architecture,\\ and develop scalable solutions for new features within a micro-mobility application.}
			\item {Migrated the company's main application from React Native to Flutter,\\ reducing technical debt and enhancing performance.}
			\item {Implemented a single sign-on (SSO) feature, leading to a 66\% reduction in operational costs.}
			\item {Developed and launched a loyalty program, resulting in a 5\% increase in trips.}
		\end{cvitems}}
	\cventry
	{Kasikorn Business-Technology Group}
	{Backend Software Engineer}
	{Bangkok, Thailand}
	{November 2020 - November 2022}
	{\begin{cvitems}
			\item {Built an online payment facilitator project which handles 300,000 transactions a day.}
			\item {Built a monitoring system that identifies and alerts the team regarding non-indexed queries,\\ resulting in a 50\% reduction in production incidents.}
			\item {Achieved a 90\% reduction in reconciliation time through code refactoring.}
			\item {Streamlined sprint planning processes by creating an EazyBI dashboard for Jira,\\ leading to a 20\% reduction in meeting time.}
		\end{cvitems}}
	\cventry
	{Accenture}
	{Technical Analyst (Intern)}
	{Bangkok, Thailand}
	{June 2019 - December 2019}
	{\begin{cvitems}
			\item {Collaborated with product owners and developers to design the working process\\ of features that will be deployed in the mobile banking application with 8 million users.}
			\item {Designed and created a Kibana dashboard that uses statistical methods to detect\\ defects in the digital lending feature, which is used by 30,000 users per day.}
		\end{cvitems}}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-5mm}
\cvsection{Technical Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ p{2.5cm} l }
				Tech Stack: & {\skill{ Kotlin, Flutter, Golang, TypeScript, node.js, React.js, PostgreSQL, MongoDB}} \\
				Platform:   & {\skill{ AWS, GCP, OpenShift, Kubernetes, Docker, Control-M}}                          \\
			\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-9mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{GCP, Flutter, Python}
	{WealthWatch}
	{\href{https://play.google.com/store/apps/details?id=com.wealthwatch.portfolioapp}{Google Play Store}}
	{}
	{Developed an application to track Thai mutual funds, facilitating investment monitoring and performance evaluation to aid investors in achieving their financial goals.}
\end{cventries}
\begin{cventries}
	\cventry
	{AWS, Golang, GraphQL, React.js}
	{Axie Breeding Calculator}
	{}
	{}
	{Developed a full-stack web application to calculate expected profits for breeding Axies in the game Axie Infinity by analyzing the top 4 highest potential combinations out of over 90,000 possibilities.}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Awards}
\begin{cvhonors}
	\cvhonor
	{RideBeam Code Stars 2022}
	{Ranked 10 th out of 90}
	{September 2022}
	\cvhonor
	{Facebook Hacker Cup 2021}
	{Ranked 1,701 th out of 6,789 in round 2}
	{September 2021}
\end{cvhonors}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Bachelor of Engineering in Industrial Engineering}
	{Chulalongkorn University}
	{Bangkok, Thailand}
	{2016 - 2020}
	{}
\end{cventries}

\let\clearpage\relax
\end{document}