% !TeX root = resume.tex
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Kavinpon} \headerlastnamestyle{Navapong} \\
	\vspace{2mm}
	{\faEnvelope\ kavinpon@hotmail.com} | {\faMobile\ +66863266507} | {\faMapMarker\ Bangkok, Thailland} | {\faLinkedin\ linkedin.com/in/kavinpon}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Work Experience}
\begin{cventries}
	\cventry
	{Kasikorn Business-Technology Group}
	{Backend Software Engineer}
	{Bangkok, Thailand}
	{November 2020 – Present}
	{\begin{cvitems}
			\item {Built an online payment facilitator project which handles 300,000 transactions a day.}
			\item {Designed and integrated new payment methods including authentication process,\\ receiving payment notifications, and receiving settlement files for the reconciliation process.}
			\item {Designed and developed the money movement flow within the system.}
			\item {Supported partner integration process between partners and the project.}
			\item {Built an internal unit test framework to reduce the cost of testing and refactoring code,\\ speeds up the development process.}
			\item {Reduced reconciliation time by 90\% through code refactoring.}
			\item {Created an EazyBI dashboard for Jira to simplify the sprint planning process,\\ reduces the time spent in the meeting by 20\%.}
		\end{cvitems}}
	\cventry
	{Accenture}
	{Technical Analyst (Intern)}
	{Bangkok, Thailand}
	{June 2019 – December 2019}
	{\begin{cvitems}
			\item {Collaborated with product owners and developers to design the working process\\ of features that will be deployed in the mobile banking application with 8 million users.}
			\item {Designed an online database that can be managed through an internal website to eliminate\\ operational loss from using an Excel database.}
			\item {Designed and created a Kibana dashboard that uses statistical methods to detect\\ defects in the digital lending feature, which is used by 30,000 users per day.}
		\end{cvitems}}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-4mm}
\cvsection{Technical Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
				Tech Stack: & {\skill{ Golang, MongoDB, SQL, React.js, TypeScript}} \\
				Platform:   & {\skill{ AWS, OpenShift, Docker, Control-M}}          \\
			\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-8mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{AWS, Golang, GraphQL, React.js}
	{Axie Breeding Calculator}
	{https://axie-tools.netlify.app/}
	{}
	{Built a full-stack web app to calculate the expected profit for breeding Axies, an in-game asset in a game called Axie Infinity, by selecting the top 4 highest possibilities from over 90,000 possible combinations.}
\end{cventries}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certificates
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Certificates}
\begin{cvcertificates}
	\cvcertificate
	{Kafka Fundamentals Accreditation}
	{Confluent}
	\cvcertificate
	{Containers, K8s and Istio on IBM Cloud}
	{IBM}
\end{cvcertificates}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Awards}
\begin{cvhonors}
	\cvhonor
	{RideBeam Code Stars 2022}
	{Ranked 10 th out of 90}
	{September 2022}
	\cvhonor
	{Facebook Hacker Cup 2021}
	{Ranked 1,701 th out of 6,789 in round 2}
	{September 2021}
\end{cvhonors}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Bachelor of Engineering in Industrial Engineering}
	{Chulalongkorn University}
	{Bangkok, Thailand}
	{2016 – 2020}
	{GPA: 3.51}
\end{cventries}

\vspace{-2mm}
\
\end{document}